
```{r, setup, echo = FALSE, message = FALSE}
knitr::opts_chunk$set(
  comment = "#>",
  tidy = FALSE,
  error = FALSE,
  fig.width = 8,
  fig.height = 8)
```

# conf

> Persistent Package Configuration

[![Linux Build Status](https://travis-ci.org/gaborcsardi/conf.svg?branch=master)](https://travis-ci.org/gaborcsardi/conf)
[![Windows Build status](https://ci.appveyor.com/api/projects/status/github/gaborcsardi/conf?svg=true)](https://ci.appveyor.com/project/gaborcsardi/conf)
[![](http://www.r-pkg.org/badges/version/conf)](http://www.r-pkg.org/pkg/conf)
[![CRAN RStudio mirror downloads](http://cranlogs.r-pkg.org/badges/conf)](http://www.r-pkg.org/pkg/conf)
[![Coverage Status](https://img.shields.io/codecov/c/github/gaborcsardi/conf/master.svg)](https://codecov.io/github/gaborcsardi/conf?branch=master)

Store the configuration of your package in the user's platform dependent
config file directory. The configuration persists across R sessions, and can
also be edited manually. Configuration files are YAML files.

## Installation

```{r eval = FALSE}
devtools::install_github("gaborcsardi/conf")
```

## Usage

```{r}
library(conf)
```

`conf` uses the `rappdirs` package (https://github.com/hadley/rappdirs) to
determine the appropriate location of the configuration file of a package.

To determine the location of the configuration file, you can use:
```{r}
conf$new(package = "mypackage")$get_path()
```

Create a configuration file by creating a `conf` object, then setting
some configuration keys in it, and writing it out to a file:
```{r eval = FALSE}
cf <- conf$new(package = "mypackage", lock = TRUE)
```

```{r echo = FALSE, results = "hide"}
cf <- conf$new(file = tempfile(), lock = TRUE)
```

```{r}
cf$set("user:id", "test-user")
cf$set("user:email", "test@acme.com")
cf$set("rversion", format(getRversion()))
```

```{r}
cf
```

```{r}
cf$save()
```

## License

MIT © RStudio Inc
